---
title: "Workshop 4"
format: html
bibliography: references.bib
---

See @fig-penguins-scatter for the penguin scatter plot.
```{r}
#| label: fig-penguins-scatter
#| fig-cap: "Body mass vs. Flipper length for three penguin species."
#| warning: false
library(ggplot2)
library(palmerpenguins)

ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point() +
  theme_minimal()
```


```{r}
#| label: tbl-penguin-summary
#| tbl-cap: "Mean body mass of penguins by species and sex."
library(dplyr)

penguins |>
  filter(!is.na(sex)) |>
  group_by(species, sex) |>
  summarise(mean_mass = mean(body_mass_g)) |>
  knitr::kable()
```

As shown in @fig-penguins-scatter, there is a clear positive correlation between flipper length and body mass. The specific averages for each group are detailed in @tbl-penguin-summary.
Parenthetical: The data was originally collected by Gorman et al. [@penguins_data].
Narrative: @penguins_data provides a high-quality penguin dataset for teaching statistics.